---
title: "Stop Report Inaccuracies"
author: "Steven Kalt"
date: "February 5, 2016"
output: html_document
---
The gps coords reported at each point when Stop_Repor == 1 is consistently down the road from where the stops actually are.  

```{r imports}
require(dplyr)
require(class)
library(vegan)
# setwd('./HackPVTA')
setwd('./Data')
```
I considered the data as a whole.
```{r file names}
monthly.files <- c('April2015.csv',
                  'January2015.csv',
                  'November2015.csv',
                  'August2015.csv',
                  'October2015.csv',
                  'December2015.csv',
                  'July2015.csv',
                  'September2015.csv',
                  'February2015.csv',
                  'June2015.csv',
                  'March2015.csv',
                  'May2015.csv')
# for these the column names are: 
column.names <- c("vehicle.ID", "time", "lat", "lon", "speed",
                  "direction",
                  "off.route.status", "comm.status", "operational.status",
                  "server.time",
                  "route", "trip", "inbound.outbound", "deviation", "onboard",
                  "vehicle.name", "run.ID", "run.name", "stop.name",
                  "operator.record.ID",
                  "route.name", "stop.report", "scheduled.headway", "target.headway",
                  "alarm.state", "GPS.status", "boards", "alights", "confidence.level",
                  "message.type.ID", "stop.dwell.time", "PTV.health.alert", "stop.ID",
                  "stationary.status", "stationary.duration")
stop.coord.directories <- c('pvta_20150111_0102',
                            'pvta_20150308_0103',
                            'pvta_20150821_0118',
                            'pvta_20151217_1050',
                            'pvta_20150306_0109',
                            'pvta_20150626_0325',
                            'pvta_20150823_0119')
stop.coord.files <- c()
for (directory in stop.coord.directories){
  stop.coord.files <- c(stop.coord.files, paste(".",
                                                "GoogleData",
                                                directory,
                                                "stops.txt",
                                                sep = "/"))
}
rm(stop.coord.directories)
```
```{r actually open a file}
# for simplicity, start with one.
month <- read.table(monthly.files[1], sep = ',', header = F)
for (c in c(1:length(column.names))){
  names(month)[c] <- column.names[c]
}

# get file of stop coords 
real.coords <- read.csv(stop.coord.files[1], stringsAsFactors = F)
names(real.coords) <- c('stop.id',
                        'stop.name',
                        'stop.desc',
                        'stop.lat',
                        'stop.lon',
                        'stop.street',
                        'stop.city',
                        'stop.region',
                        'stop.postcode',
                        'stop.country',
                        'zone.id')
real.coords <- real.coords[,c('stop.name','stop.lat','stop.lon')]
# real.coords$stop.name <- unlist(strsplit(real.coords$stop.name, '[(]'))
```

```{r where to find stops in data}
# false starts
summary(month$stationary.duration)
summary(month$stationary.status)

#potential starts: when are people boarding, exiting, or when is a stop reported?
has.boarding <- month[month$boards > 0 | month$alights > 0,]
has.dwelt <- month[month$stop.dwell.time > 0,]
table(month$stop.report)
table(has.dwelt$stop.report)
table(has.boarding$stop.report)
#based on these filters, all stop reports != 0 are somewhat meaningful-- no stop report
# is the mode.
stop.reported <- month[month$stop.report != 0,]
stop.estd.coords <- as.data.frame(summarise(group_by(stop.reported, stop.name), 
                                            lat = median(lat),
                                            lon = median(lon)))
stop.estd.coords$stop.name[] <- lapply(stop.estd.coords$stop.name, as.character)
deltas <- as.data.frame(summarise(group_by(stop.reported, stop.name, lat, lon)))
```

```{r match stop names with google names}
CloseBy <- function(a,b, epsilon, mode="square"){
  #a function that is meant to find very near neighbors within a a distance or radius 
  #of a pair of gps coordinates
  #Args:
  #   a: the training gps coords
  #   b: the test gps coords
  #Returns:
  #   TRUE if the test point is in the range, FALSE otherwise
  if (mode == "square"){
    coord.diff <- abs(a - b)
    return(coord.diff[1] <= epsilon & coord.diff[2] <= epsilon)
  } else {
    coord.diff <- sqrt((a[1] - b[1])^2 + (a[2] - b[2])^2)
    return(coord.diff >= epsilon)
  }
}
possible.matches <- list()
for (c1 in c(1:nrow(real.coords))){
  for (c2 in c(1:nrow(stop.estd.coords))){
    if (CloseBy(stop.estd.coords[c2, c(2,3)],
                real.coords[c1, c(2,3)],
                epsilon = .00005)){
      print(c(stop.estd.coords[c2,1], real.coords[c1, 1]))
      # possible.matches[[stop.estd.coords[c2,1]]] <- real.coords[c1, 1]
    }
  }
}
# TODO question sanity, iteratively search, eliminate stops

for (i in c(1:nrow(stop.estd.coords))){
  print(
    real.coords$stop.name[
      sum(abs(real.coords[i,c(2,3)] - stop.estd.coords[i, c(2,3)])) < .00001])
}
# matching <- knn1(train = real.coords[,c(2,3)],
#                 test =stop.estd.coords[,2,3] ,
#                 cl = real.coords$stop.name)
row.names(real.coords) <- real.coords$stop.name
rbind(real.coords,)
for (r in c(1:nrow(stop.estd.coords))){
  for (r2 in c(1:nrow(real.coords))){
    if dist()
  }
}
summary(month$stop.dwell.time) #! 
# stationary.busses <- month[month$stationary.duration > 0,] # empty
# stationary.busses2 <- month[month$stationary.duration > 0,] # empty
# knn(train = real.coords, )
